\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Leonardo B. Tosin}
\address{Garibaldi, RS - Brazil}
\address{leotosin.com.br  \\ leob.tosin@hotmail.com}

\begin{document}

\begin{rSection}{Education}

{\bf Universidade de Caxias do Sul(UCS), Bento Gon\c{c}alves} \hfill {\em January 2013 - 2022} 
\\ Computer Science Bachelor

\end{rSection}

\begin{rSection}{Resume}
Currently working as a Dynamics AX and .NET software developer at my regular dayline. And Android developer and enthusiast at my free time. \\
I'm at software development for arround 4+ years, working in different fields, web, mobile and desktop applications. Always interested on learning new technologies and improving personal and technical skills.  \\
At the moment, interested on native mobile development, webservices, distributed systems, serverless,  big data and backend software development.
 \end{rSection}

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Favorite Programming Languages  \ &  Kotlin,  Java and Swift \\
Other programming languages \ & .NET, C/C++, Python, Ruby, PHP and JS\\
Software Architecture \ &  MVVM, MVC, MVI and MVP\\
Agile software development \ & Scrum, ICONIX and XP \\
Code versioning \ & Git and SVN \\
Cloud \ & Azure and Heroku \\ 
\end{tabular}

\end{rSection}

\begin{rSection}{working experience}

\begin{rSubsection}{NuvolaHost Servi\c{c}os de TI}{April 2017 - September 2019}{Full-Stack Software Developer}{}
\item Maintainer of the management system sell by the company called pGestor, from the development of new features, improvements and corrections to the attendance, support and training of the system's user. Ocsionally worked with  responsive websites design and the mail marketing system called Envie certo.
\end{rSubsection}

\begin{rSubsection}{Cooperativa Santa Clara}{September 2019 -  Currently}{Mid-Level Software Developer}{}
\item Maintainer of the management system of the company on the Dynamics AX 2012, and build new stuff using it's embedded language, X++. Maintance of APIs build on .NET and NodeJS. And build reports using SSRS Reports Server.
\end{rSubsection}


\end{rSection}



\begin{rSection}{Voluntary work} 
\item President of the \textit{diret\'orio acad\^emico de Ci\^encia da Computa\c{c}\~ao} from the period 2017-2018.
\item President of the \textit{Associa\c{c}\~ao Garibaldense de Estudantes no Campus Universit\'ario da Regi\~ao dos Vinhedos} from the period 2017-2019.
\end{rSection}


\end{document}
